### 2018-12-18 README.Rmd
attempt to update pkgdown site

## Usage 
### Data
The package contains four overlapping data sets:

>>>>

## Usage 
Two function prefixes are used in `areal` to allow users to take advantage of RStudio's auto complete functionality:

* `ar_` - data and functions that are used for multiple interpolation methods
* `aw_` - functions that are used specifically for areal weighted interpolation

### Data
The package contains four overlapping data sets:
